Democracy, Public Support, and Measurement Uncertainty

### 2021-04-29 paper/dcpo_demsupport.Rmd
clean claassen_replication and get country number

```{r claassenUncertaintyAJPS}
claassen_replication_input$data <- claassen_replication_input$data %>% 
  janitor::clean_names() %>% 
  DCPOtools::with_min_yrs(2)

>>>>

```{r claassenUncertaintyAJPS}
claassen_replication <- read_csv(here::here("data", "claassen_replication.csv"),
                   col_types = "cdcddcdc") %>% 
  janitor::clean_names() %>% 
  DCPOtools::with_min_yrs(2)

length(unique(claassen_replication$country))
